\usefont{OT1}{bch}{b}{n} \normalfont \normalsize \textsc{School of random department names} \\ [25pt] \horrule{0.5pt} \\[0.4cm] \huge This is the title of the template report \\ \horrule{2pt} \\[0.5cm]

### 2018-06-05 Report/notes.tex
report change

	\begin{figure}
		\begin{tikzpicture}[->,>=stealth',shorten >=1pt,auto,node distance=3.0cm,
		semithick]
		\tikzstyle{every state}=[fill=red,draw=none,text=white]

@@

		\end{tikzpicture}
		\caption{Old Phase Type Model, Production isn't enabled in full queue}
		\label{fig:queue_new}
	\end{figure}

@@

\clearpage
\subsection[epsilon termination]{Condition on epsilon termination}
$$\epsilon \leq \frac{\epsilon_{wanted}}{k}$$
$$\forall s \in S, \epsilon \leq Pr(s)$$
$$\epsilon \leq median(Pr(s))$$
$$\epsilon \leq 1stQuartile(Pr(s))$$
$$\epsilon \leq 1stDecile(Pr(s))$$
$$CDF(t-\delta) \leq \epsilon$$
$$\epsilon \leq \frac{1}{|S|}$$
$$\epsilon \leq v = \frac{k}{\lambda^2} = \frac{m^2}{k}$$

>>>>

\begin{figure}
	\centering
	\begin{tikzpicture}[->,>=stealth',shorten >=1pt,auto,node distance=2.5cm,
	semithick]
	\tikzstyle{every state}=[fill=red,draw=none,text=white]

@@

	\end{tikzpicture}
	\caption{Old Phase Type Model, Production isn't enabled in full queue}
	\label{fig:queue_new}
\end{figure}
\clearpage

@@

\clearpage
\subsection[epsilon termination]{Condition on epsilon termination}
$$\epsilon \leq \frac{\epsilon_{wanted}}{k}$$
$$\forall s \in S, \epsilon \leq Pr(s)$$
$$\epsilon \leq \frac{1}{|S|}$$
$$\epsilon \leq \sigma = \sqrt{v}, v = \frac{k}{\lambda^2} = \frac{m^2}{k}$$
$$\epsilon \leq median(Pr(s))$$
$$\epsilon \leq 1stQuartile(Pr(s))$$
$$\epsilon \leq 1stDecile(Pr(s))$$
$$CDF(t-\delta) \leq \epsilon$$
